<small> Supplementary materials for the main submission entitled - <br><br> Clustering time series based on probability distributions across temporal granularities

### 2021-11-09 paper-supplementary.Rmd
supplementary material till interaction updated

## Plot displaying missing observations

\noindent The data set contains 13,735 customers, of which 8,685 have no missing values and the remaining $5,050 customers have at least one missing value. We wanted to see if there was any structure to these missing observations, so we plotted them over time in Figure \ref{fig:missing-data}. Each row represents a customer, with the blank indicating non-missing values and the shapes indicating missing values. Figure 9 of @wang2019tsibble inspired this plot. For the most part, it appears that data for September and October 2012 are missing. Otherwise, missingness can occur at any time and there is no pattern.

```{r missing-data}
knitr::include_graphics("figs/missing-data-5050.png")
```

@@

### Interaction of granularities

Consider a case in which there are only two interacting granularities of interest, $g1$ and $g2$. In contrast to the previous situation, when we could study distributions across $n_{g_1} + n_{g_2} = 5$ separate categories, with interaction, we must evaluate the distribution of the $n_{g_1}*n_{g_2}=6$ combination of categories. Consider the $4$ designs in Figure \ref{fig:interaction-gran}, where various distributions are assumed for different combinations of categories, resulting in different designs. Design $D1$ exhibits no change in distributions across $g1$ or $g2$, whereas Designs $D2$ and $D3$ alter across only $g1$ and $g2$, respectively. D4 varies across both $g1$ and $g2$ categories. D3 and D4 appear similar based on their relative differences across consecutive categories, but $D4$ also changes across facets, unlike $D3$, which has all facets look the same.

```{r interaction-gran, fig.cap = "Distribution of the simulated variable across $g1$ conditional on $g2$ is shown through boxplots for 4 designs. D1 has no change in distributions across different categories of $g1$ or $g2$, while D2 and D3 change across only $g1$ and $g2$ respectively. D4 changes across categories of both $g1$ and $g2$."}

>>>>

(ref:missing-data) Investigating the temporal location of missing values for customers who have implicit missing values. There are $13,735$ customers in the data set, with 8,685 having no missing values and the remaining $5,050$ having at least one missing value. Each cross represents a missed observation in time, while the line connecting two dots represents continuous missingness over time. Missing values occur at random times and do not appear to follow a pattern, although there is a higher concentration of missing values in September and October 2012 for the majority of customers. This plot is inspired by @wang2020tsibble.

```{r missing-data, fig.cap="(ref:missing-data)"}
knitr::include_graphics("figs/missing-data-5050.png")
```

@@

<!-- ### Interaction of granularities -->

<!-- Consider a case in which there are only two interacting granularities of interest, $g1$ and $g2$. In contrast to the previous situation, when we could study distributions across $n_{g_1} + n_{g_2} = 5$ separate categories, with interaction, we must evaluate the distribution of the $n_{g_1}*n_{g_2}=6$ combination of categories. Consider the $4$ designs in Figure \ref{fig:interaction-gran}, where various distributions are assumed for different combinations of categories, resulting in different designs. Design $D1$ exhibits no change in distributions across $g1$ or $g2$, whereas Designs $D2$ and $D3$ alter across only $g1$ and $g2$, respectively. D4 varies across both $g1$ and $g2$ categories. D3 and D4 appear similar based on their relative differences across consecutive categories, but $D4$ also changes across facets, unlike $D3$, which has all facets look the same. -->

```{r interaction-gran, fig.cap = "The distribution of simulated variable across $g1$ conditional on $g2$ is shown through boxplots for 4 designs to extend the proposed validation designs when two granularities of interest interact. D1 has no change in distributions across different categories of $g1$ or $g2$, while D2 and D3 change across only $g1$ and $g2$ respectively. D4 changes across categories of both $g1$ and $g2$."}
